Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State with Multivariate Techniques

### 2015-12-04 paper/sec-pileup.tex
more work on paper

Let us begin by comparing
representative signal distributions with
and without PU, with $\la n_{\rm PU}\ra=80$ in the
former
case (and SK subtraction).
%
In Fig.~\ref{fig:m_H_PU} we show the invariant mass distribution
of the leading and subleading Higgs candidates, corresponding to both
the boosted
and resolved categories.
%
These distributions are plotted after the $b$-tagging, that is,
before they are used as input to the MVA.
%
As we can see, in the boosted category, the residual effects of PU
after the {\tt SoftKiller} subtraction are rather mild,
with the position of the Higgs mass peaks essentially
unchanged, and only a moderate distortion of the
distribution found.
%
The effects are more important for the resolved category, where PU
shifts the Higgs peak by an amount $\Delta m_h \simeq 5$ GeV.

@@

It is also interesting to quantify how
the relative differences between
signal over background distributions are affected in 
the presence of PU.
%
Considering first of all the boosted category,
in Fig.~\ref{fig:signal-vs-back-boosted} we compare
various kinematical distributions for signal and background events,
     with and without PU: the invariant mass and the $p_T$ of the leading
     Higgs candidate, the 2-jettines $\tau_{21}$ and $\sqrt{d_{12}}$,
     $k_T$ splitting scale, Eq.~(\ref{eq:ktsplitting}),
     for the leading Higgs candidate.
     %
     While for signal distributions the effects of PU after SK subtraction are small,
     differences are more marked for the background distributions, where
     the shapes of the distributions with and without background can be substantially
     different.
     %
     We note however that the fact that signal and background distribution exhibit
     rather different behaviors is maintained in the presence of PU.

>>>>

First of all, let us validate both the implementation of our
simulation of PU, as well as the SK subtraction, by comparing the
invariant mass distributions of Higgs candidates in signal
events in the resolved category.
%
In Fig.~\ref{fig:PUvalidation} we show three curves: without PU,
with PU $\la n_{PU}\ra=80$ but without any subtraction, and the
same but now with the SK subtraction.
%
As expected, if PU is not subtracted there is a large shift in the Higgs mass
peak, by about 40 GeV.
%
Once SK subtraction is performed, we recover a distribution much closer
to the original ones, with only a small shift of $\simeq 5$ GeV in the mass
distribution.
%
As we will see below, the performance of SK is even better in the boosted category,
since the effects of PU are mitigated for high $p_T$ jets.

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
  \includegraphics[width=0.68\textwidth]{plots/m_htot_res_signal_PUnoSK.pdf}
    \caption{\small
    The invariant mass distributions of Higgs candidates in signal
events, in the resolved category, comparing the results without PU,
with PU $\la n_{PU}\ra=80$ but without any subtraction, and the
corresponding results now with SK subtraction.
}
\label{fig:PUvalidation}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

Next, we compare more
 signal distributions with
and without PU, with $\la n_{\rm PU}\ra=80$ in the
former
case (and SK subtraction).
%
In Fig.~\ref{fig:m_H_PU} we show the invariant mass distribution
of the leading and subleading Higgs candidates, corresponding to both
the boosted
and resolved categories.
%
These distributions are plotted after the $b$-tagging, that is,
before they are used as input to the MVA.
%
As we can see, in the boosted category, the residual effects of PU
after the {\tt SoftKiller} subtraction are rather mild,
with the position of the Higgs mass peaks essentially
unchanged, and only a moderate distortion of the
distribution found.
%
The effects are more important for the resolved category, where PU
shifts the Higgs peak by an amount $\Delta m_h \simeq 5$ GeV.

@@

It is also interesting to quantify how
the relative differences between
signal over background distributions are affected in 
the presence of PU.
%
Considering first of all the boosted category,
in Fig.~\ref{fig:signal-vs-back-boosted} we compare
various kinematical distributions for signal and background events,
     with and without PU: the invariant mass and the $p_T$ of the leading
     Higgs candidate, the 2-jettiness $\tau_{21}$ and $\sqrt{d_{12}}$,
     $k_T$ splitting scale, Eq.~(\ref{eq:ktsplitting}),
     for the leading Higgs candidate.
     %
     While for signal distributions the effects of PU after SK subtraction are small,
     differences are more marked for the background distributions, where
     the shapes of the distributions with and without background can be substantially
     different.
     %
     We note however that the fact that signal and background distribution exhibit
     rather different behaviors is maintained in the presence of PU.
